\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{mathptmx}
\usepackage{geometry}
\usepackage{titling}
\setlength{\topskip}{0mm}
\setlength{\droptitle}{-8em} 
\title{{\large\textbf{\normalsize PROBLEM 7 : TEST CASES REVIEW }}}
\section*{{REPOSITORY DETAILS}}
{{\normalsize https://github.com/ManushreeMallaraju/Manushree-SOEN\_6011\_Project
\\
https://github.com/mjmohammadi1/SOEN6011}}
 
\begin{document}
\section*{{PROBLEM 7 : TEST CASES REVIEW}}
    I did the Test Case review of Jafar's function, F8 test.java. Test Cases are reviewed with the criteria how they achieve different coverages and analysis. 
Inputs used for review: Requirements Document and Java code, Java Test cases from Jafar's repository.


\section*{\normalsize Summary of Test Cases Review}

\textbf{Requirements Coverage: } 
\\$\bullet$~ 	REQ 1 and REQ 3 are covered with Testcases implemented in BetaTest.java, GamaTest.java. 
\\
$\bullet$~ 	Test case for REQ 2 is missing. 
\\
$\bullet$~	REQ 1 and REQ 3 can be covered with multiple inputs to check accuracy of implementation with values including MAX and MIN values of positive real numbers.
\\
 Requirement Coverage is required as part of SEP to make ensure all the requirements are tested and validated in compliance with the given standards so as to achieve the desired behavior from the Program.
\\

 \textbf{Code Coverage:} 
 \\$\bullet$~	The test cases used will not cover the whole code which will remain untested. Test Cases should be added to get the maximum coverage of code to find the dead code in the logic.
\\
Code Coverage will ensure that there is no logic written which was not intended or which is unable to cover with the specific type of inputs given by the user.
\\

 \textbf{Robustness:} \\
 $\bullet$~	Test cases with invalid inputs should be added to check exception handling process. Inputs such strings or characters can be given instead of real numbers to check if the program crashes.
\\
Test cases with robust input is need to check how the program responses when user provides improper inputs.
\\

 \textbf{Condition/Decision Coverage:} 
\\
$\bullet$~	Test Cases should be added to cover each and every condition written in the logic. These test cases will ensure there is Logic which is not being used or getting satisfied during run time.
\\
Test Cases with different values which covers all TRUE and FALSE cases of all the conditions (IF, WHILE, FOR...) present in the code will find the uncovered conditions.
$\bullet$~ \textbf{         } :


\section*{\normalsize References}

http://www.softwaretestingclass.com/test-case-review-process-tips-and-tricks/
\\
http://softwaretestingtimes.com/2010/06/test-case-review-process-tips.html\\

https://medium.com/palantir/code-review-best-practices-19e02780015f



\end{document}